---
title: "norspis-create-reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{norspis-create-reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Purpose of document

This file shows how to make printable report in PDF-formats. We currently have two options:

* Making a report for each hospital department (norspis-periodisk-rapport.Rmd)
* Making a report for use in NorSpis (norspis-oversiktsrapport.Rmd)

The .Rmd documents above that we use here are saved in the inst folder of norspis2. And we use the render_report.R function in norspis2, which is made for the purpose of running the .Rmd-documents. 


# How to use this .Rmd-document

Just run the relevant code snippet below. You do not need to knit this entire .Rmd-document. 


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(norspis2)
```


Make report for all RESH-id's
```{r}
#getwd()

for(reshID in unique(DL$RegData2$AvdRESH)){
  
  norspis2::render_report(reshID = reshID)
}

```

